Le titre

### 2022-08-28 Manuscrit Thèse/chapter 4/Chapter 4.tex
lalalere

Based on these depolarization measurements under transverse magnetic field, we expect that the depolarization at low magnetic fields behave similarly, and that the difference in NV polarization between the $\mathbf{B}=0$ region and $\mathbf{B} \neq 0$ region is caused by (in order of importance):
\begin{enumerate}
\item The lift of degeneracy between the four classes caused by the projection of the magnetic field on the different NV axis.
\item The double flips between the nearly resonant $\ket{+}$ and $\ket{-}$ states at low magnetic field.
\item The change of the Hamiltonian eigenbasis from $\{\ket{0}, \ket{\pm} \}$ in the electric field dominated region to $\{\ket{0}, \ket{\pm 1} \}$ in the magnetic field dominated region, and the incident change in $T_2^*$.
\end{enumerate}

@@

Fig.

\subsection{Characterization of the experiment}
sensi, dépendence sensi angle, variance d'allan
\subsection{Comparison with other magnetometry protocol}
Budker : mesurer vite deuf les pentes
\section{Conclusion and perspectives}
- Improvement to the sensitivity : Scale up (les deux papiers sur le picoTesla mW, avec les deux systèmes), material optimization (15N !, [NV] concentration, )

>>>>

We have here quantitatively measured different depolarization contributions for a single class submitted to purely transverse magnetic field. We expect that the depolarization for low magnetic fields behave similarly, and that the difference in NV polarization between the $\mathbf{B}=0$ region and $\mathbf{B} \neq 0$ region is caused by (in order of importance):
\begin{enumerate}
\item The lift of degeneracy between the four classes caused by the projection of the magnetic field on the different NV axis.
\item The double flips between the nearly resonant $\ket{+}$ and $\ket{-}$ states at low magnetic field.
\item The change of the Hamiltonian eigenbasis from $\{\ket{0}, \ket{\pm} \}$ in the electric field dominated region to $\{\ket{0}, \ket{\pm 1} \}$ in the magnetic field dominated region, and the incident change in $T_2^*$.
\end{enumerate}

@@

Fig. \ref{setup magneto} shows the principle of the LFDM protocol. The experimental setup is similar to the one presented in Fig. [REF] with the exception that there are no microwaves, and that the magnetic field generated by the electro-magnet contains both a DC or slowly variable component $B_0$ and an oscillating component $\delta B$ used for the modulation. We typically use a modulation frequency $f_{\rm mod} \approx 1\ \rm kHz$, the same value we use for ODMR measurements. The main voltage $V_0$ responsible for the DC field and the oscillating voltage $\delta V$ responsible for the AC field are summed via a homemade bias tee.

Fig. \ref{setup magneto}-b) and c) show respectively the PL measured directly on the photodiode and the lock-in signal when the DC magnetic field is slowly varied ($f_{\rm scan}<1\ \rm Hz$) from -150 to +150 G. The magnetic field was randomly oriented with respect to the NV axes and did not match any particular crystalline axis.

Both AC (up to $\sim$ 10 kHz) and DC-magnetometry are possible with this setup. to improve the sensitivity however, an AC field needs to be added for the DC sensing, and inversely a DC field needs to be added for the AC sensing. Both of these added fields are typically of a few G for optimal performances, which limits the ultra-low field applications.

Fig. [A FAIRE] shows how the AC and DC sensing work for LFDM. For DC sensing, we want to use an oscillating field with an amplitude that matches the width of the PL dip $|\delta B| \approx \sigma$, in order to maximize the slope of the lock-in signal around $B_0=0$. For AC sensing, we want to use a static field $B_0=\sigma$ corresponding to the region where the lock-in signal is most sensitive to AC field.

\subsection{Characterization of the experiment}
We will now look at the performances of the LFDM protocol before comparing it to the other magnetometry protocols. The characterization was only done for DC sensing, but DC and AC are supposed to be symmetrical. The sample used for the characterization were 15 $\mu$m micro-diamond bought as is from Adamas nanodiamond (see the sample section [REF] for more information).
\subsubsection{Sensitivity}

sensi, dépendence sensi angle, variance d'allan
\subsection{Comparison with other magnetometry protocol}
Budker : mesurer vite deuf les pentes
\section{Conclusion and perspectives}
- Improvement to the sensitivity : Scale up (les deux papiers sur le picoTesla mW, avec les deux systèmes), material optimization (15N !, [NV] concentration, )
